Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-08-13 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
x paper

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych)

@@

## 3. Correlations

```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}

@@

# classroom questionnaire
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LI06_05, 
                LM01_01:LM01_08, # classroom management
                LP01_01:LP01_08) %>% # non- & paraverbal communication
  filter(!LI06_05 %in% c(201, 223, 232)) %>% # exclude ID with no eye tracking data
  rename(Participant = LI06_05) %>% 
  group_by(Participant) %>% 
  transmute(Participant = Participant,
            "Quest_All" = round(mean(c_across(starts_with("L")), na.rm = TRUE), 2),
            "Quest_classroom_management" = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
            "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2)
            )

# create a big data frame with all measures 
#put all data frames into list
df_list <- list(df_demo,
                  df_aoi_numb_dur,
                  df_aoi_stud,
                  df_aoi_disrup,
                  df_sri,
                  df_sjt,
                  df_quest)

#merge all data frames in list
df_merge <-
  df_list %>% reduce(full_join, by='Participant')

>>>>

library(needs)
needs(tidyverse,
      lubridate,
      viridis,
      grid,
      gridExtra,
      cowplot,
      readxl,
      ARTofR,
      moments,
      ltm,
      sjPlot,
      kableExtra,
      xtable,
      DescTools,
      formattable,
      psych,
      apaTables)

@@

## 3. Correlations
```{r correlations, echo=FALSE, message=FALSE, warning=FALSE}

@@

# classroom questionnaire
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(LI06_05, LM01_01:LM01_08, # classroom management
                LP01_01:LP01_08) %>% # non- & paraverbal communication
  filter(!LI06_05 %in% c(201, 223, 232)) %>% # exclude ID with no eye tracking data
  rename(Participant = LI06_05) %>%
  group_by(Participant) %>%
  transmute(
    Participant = Participant,
    "Quest_All" = round(mean(c_across(starts_with(
      "L"
    )), na.rm = TRUE), 2),
    "Quest_classroom_management" = round(mean(c_across(starts_with(
      "LM"
    )), na.rm = TRUE), 2),
    "Quest_non_paraverbal_communication" = round(mean(c_across(starts_with(
      "LP"
    )), na.rm = TRUE), 2)
  )

# create a big data frame with all measures 
# put all data frames into list
df_list <- list(df_demo,
                  df_aoi_numb_dur,
                  df_aoi_stud,
                  df_aoi_disrup,
                  df_sri,
                  df_sjt,
                  df_quest)

# merge all data frames in list
df_merge <-
  df_list %>% reduce(full_join, by='Participant') %>% 
  dplyr::select(.,
                -"Participant")

# create a correlation matrix
cor_tab <- 
  df_merge %>% 
  cor(method = "spearman") %>% 
  round(., digits = 2)

# create a scatter plot 
# pairs(~ Gender + 
#         Age + 
#         `Teaching Experience` + 
#         Sum_number_fixation + 
#         Stud_number_fixation + 
#         Number_of_fixations.Disruptive_Person + 
#         Average_duration_mtu + 
#         Average_duration_stud + 
#         Average_duration_disrup + 
#         GRI_mtu + 
#         GRI_stud + 
#         GRI_disrup + 
#         Mean_disrupption_appraisal + 
#         Mean_confidence_appraisal + 
#         Mean_prevalence_rating + 
#         SJT_Monitoring + 
#         SJT_Managing_momentum + 
#         SJT_Rules_routines + 
#         SJT_All + 
#         Quest_classroom_management + 
#         Quest_non_paraverbal_communication + 
#         Quest_All,
#       upper.panel = NULL,
#       pch = 20,
#       cex = 3, 
#       main = "Correlation Table Expertise Measures",
#       col = Gender)

# apa.cor.table(cor_tab)
